\ \break Automatikus korpuszépítés tulajdonnév-felismerés céljára

### 2013-01-03 paper/MSZNY2013/mszny_slides.tex
I'm going home.

\subsection*{Motivation}
\begin{frame}{Motivation}
  \bigskip

  \begin{itemize}
  \item Our goal is to create a large NE annotated corpus, automatically
        generated from WP articles.
  \smallskip
  \vitem Our method is similar to Nothman et al. (2008)
  \vitem The process consists of four steps:
    \begin{enumerate}
    \vitem Classify WP articles into entity classes.
    \vitem \textit{Parse WP and split articles into sentences.}
    \vitem Label named entities in the text.
    \vitem Select the sentences for inclusion in the corpus.
    \end{enumerate}
  \end{itemize}
\end{frame}

\subsection{Articles to Entities}
\begin{frame}{Articles to Entities}
  \bigskip
  Our method is based on thinking of WP articles as NEs.
  \smallskip
  \begin{itemize}
  \vitem Usual approach: semi-supervised learning (infoboxes, first sentence)
  \vitem Our approach: create entity list from DBpedia
    \begin{itemize}
    \vitem OWL ontology with 320 classes
    \vitem We take the most specific class
    \vitem Manual mapping to CoNLL categories that exploits inheritence
    \end{itemize}
  \item Decreased coverage, increased precision
  \end{itemize}
\end{frame}

>>>>

\subsection*{Motiváció}
\begin{frame}{Motiváció}
  \bigskip

  \begin{itemize}
  \item Célunk egy NE korpusz készítése automatikusan, a Wikipédia cikkei alapján
% TODO: WP két tulajdonsága
  \smallskip
  \vitem Módszerünk hasonló Nothman et al. (2008)-hoz
  \vitem A korpuszépítés a következő lépésekből áll:
    \begin{enumerate}
    \vitem a Wikipédia-cikkeket entitásosztályokba soroljuk;
    \vitem a cikkeket mondatokra bontjuk;
    \vitem felcímkézzük a tulajdonneveket a szövegben;
    \vitem kiszűrjük a rossz minőségű mondatokat.
    \end{enumerate}
  \end{itemize}
\end{frame}

\subsection{Cikkek, mint entitások}
\begin{frame}{Cikkek, mint entitások}
  \bigskip
  Our method is based on thinking of WP articles as NEs.
  \smallskip
  \begin{itemize}
  \vitem Usual approach: semi-supervised learning (infoboxes, first sentence)
  \vitem Our approach: create entity list from DBpedia
    \begin{itemize}
    \vitem OWL ontology with 320 classes
    \vitem We take the most specific class
    \vitem Manual mapping to CoNLL categories that exploits inheritence
    \end{itemize}
  \item Decreased coverage, increased precision
  \end{itemize}
\end{frame}
